Distances

### 2020-05-08 03_distances.Rmd
Repair park points creator, and rewrite points files

To calculate network-based distances between block group / tract centroids and
park boundaries, we employ the `osmnx` library for Python. This is a relatively
new package that allows users to retrieve networks from OpenStreetMap and 
compute shortest paths using Python's other network libraries. We retrieve
a walk network for New York City, and re-project it to UTM zone 18N

@@

```{r park_points, eval = FALSE}
open_spaces <- open_spaces %>%
  filter(id == "M010") %>%
  select(id)  %>%
  # some polygons are way too detailed, so we want to simplify to 100 foot resolution
  st_simplify(dTolerance = 100, preserveTopology = TRUE)
# some parks have multiple polygons. We need these to be simpler individual features 
poly_from_multi <- open_spaces %>%
  filter(st_geometry_type(geometry) == "MULTIPOLYGON") %>%
  st_cast("POLYGON")
linestrings <- open_spaces %>%
  # join the original polygons back with the simplified multipolygons
  filter(st_geometry_type(geometry) != "MULTIPOLYGON") %>%
  rbind(poly_from_multi) %>%
  # cast the polygons to a linestring of the park perimeter
  st_cast("LINESTRING", group_or_split = TRUE) 
point_samples <- linestrings %>%
  # sample points along the line, one point per 1000 feet.
  st_line_sample(density = 1/500) 
# append open space id
open_space_points <- tibble(id = linestrings$id, geometry = point_samples) %>%
  st_as_sf() %>%
  st_cast(to = "POINT")
```

```{r open_space_points, echo = FALSE}
park_points <- read_csv("data/park_points.csv") %>%
  st_as_sf(coords = c("LONGITUDE", "LATITUDE"), crs = 32618)
```

@@

>>>>

To calculate network-based distances between block group / tract centroids and
park boundaries, we employ the `osmnx` library for Python. This is a relatively
new package that allows users to retrieve networks from OpenStreetMap and 
compute shortest paths using Python's other network libraries. We retrieve
a walk network for New York City, and re-project it to UTM zone 18N.

@@

```{r park_points, eval = FALSE}
# get park boundary polygon
park_boundaries <- open_spaces %>%
  select(id)  %>%

  # some polygons are way too detailed, so we want to simplify to 100 foot resolution
  st_simplify(dTolerance = 100, preserveTopology = TRUE) %>%

  # need to convert everything to multipolygons to get multiple rows per shape
  st_cast("MULTIPOLYGON") %>%

  st_cast("POLYGON") %>%

  # cast the polygons to a linestring of the park perimeter
  st_cast("LINESTRING", group_or_split = TRUE)

point_samples <- park_boundaries %>%
  # sample points along the line, one point per 500 feet.
  st_line_sample(density = 1/500)

# append open space id and coerce to single point per row
park_points <- st_sf(id = park_boundaries$id, geometry = point_samples)  %>%
  st_as_sf() %>%
  st_cast(to = "POINT")
```

@@

```{r write_python_files}

write_points_file <- function(points, file){
  points %>% 
    st_transform(4326) %>%
    mutate(
      LATITUDE = st_coordinates(.)[, 2],
      LONGITUDE = st_coordinates(.)[, 1]
    ) %>%
    st_transform(32618) %>%
    mutate(
      Y = st_coordinates(.)[, 2],
      X = st_coordinates(.)[, 1]
    ) %>%
    st_set_geometry(NULL) %>%
    write_csv(file)
}

park_points     %>% write_points_file("data/park_points.csv")
bg_centroids    %>% write_points_file("data/bg_centroids.csv")
tract_centroids %>% write_points_file("data/tract_centroids.csv")

```
